How Slow do my Transient Type Checks Go?

### 2019-08-17 paper.tex
Fix type type to two type
Signed-off-by: Stefan Marr <git@stefan-marr.de>

By inspecting graphs of the performance of where only one type annotation is present, we can easily identify type annotations that likely have a significant effect on performance. By then inspecting the typing lattice graphs colour coded based on whether such type annotation was present or not, we were often able to notice patterns. In particular, these patterns suggested the just one or type type annotations are likely responsible for the bimodal performance and most of the overhead caused by Moth's transient type checking. Though every type annotation that appeared to have a significant effect across the typing lattice also showed a significant performance effect when no other typing annotations where present, the converse did not hold.

>>>>

By inspecting graphs of the performance of where only one type annotation is present, we can easily identify type annotations that likely have a significant effect on performance. By then inspecting the typing lattice graphs colour coded based on whether such type annotation was present or not, we were often able to notice patterns.
In particular, these patterns suggested the just one or two type annotations are likely responsible for the bimodal performance and most of the overhead caused by Moth's transient type checking.
Though every type annotation that appeared to have a significant effect across the typing lattice also showed a significant performance effect when no other typing annotations where present, the converse did not hold.
